Do motif roles provide unique information about species risk of extinction?

### 2021-06-04 manuscript/motifs_vs_degree.tex
All old changes have been recovered as far as I can tell.

    %\subsection*{3 Global scale network properties are known to affect stability}
    The global structural properties of ecological networks have implications for their functioning \citep{Petchey2002}, stability \citep{Allesina2012} and robustness to disturbances \citep{Dunne2002d, Eklof2006}. For example, more highly connected networks are more resistant to secondary extinctions \citep{Dunne2002d, Eklof2006} and a modular organization where some groups of species are tightly interconnected with limited connections between groups can limit the propagation of disturbances \citep{}.
    %\subsection*{4 meso-scale nw propoerties also affect stability}
    Structural properties on the local scale, i.e. properties of single species, are also well-studied and there is consensus that species with high trophic levels, few prey (low in-degree), and low abundances are generally at higher risks of secondary extinction \citep{binzer2011susceptibility}. However, in-degree and trophic level are both relatively coarse descriptions of a species' role within its food-web~\citep{Cirtwill2018FoodWebs}. 
    For example, specialists may not necessarily have a high risk of extinction if it consumes a basal resource which is at low risk of being affected of disturbance. On the other hand, a consumer with low trophic level may still be at high risk of extinction if it consumes few preys or prey which possess high risk of being affected by disturbance.

>>>>

    %\subsection*{3 Global scale network properties are known to affect stability}
    The global structural properties of ecological networks have implications for their functioning \citep{Petchey2002}, stability \citep{Allesina2012} and robustness to disturbances \citep{Dunne2002d, Eklof2006}. For example, more highly connected networks are more resistant to secondary extinctions \citep{Dunne2002d, Eklof2006} and a modular organization where some groups of species are tightly interconnected with limited connections between groups can limit the propagation of disturbances \citep{}.
    %\subsection*{4 meso-scale nw propoerties also affect stability}
    Structural properties on the local scale, i.e. properties of single species, are also well-studied and there is consensus that species with high trophic levels, few prey (low in-degree), and low abundances are generally at higher risks of secondary extinction \citep{binzer2011susceptibility}. However, in-degree and trophic level are both relatively coarse descriptions of a species' role within its food-web~\citep{Cirtwill2018FoodWebs}. 
    For example, specialists may not necessarily have a high risk of extinction if it consumes a basal resource which is at low risk of being affected of disturbance. On the other hand, a consumer with low trophic level may still be at high risk of extinction if it consumes few prey species or prey which possess high risk of being affected by disturbance.
